In figure \ref{fig:ctrdoi-20} we see the CTR improves (as in decreases) with increasing amounts of wrapping by 20 ps; from unwrapped, to partially wrapped and finally to wrapped. This is due to increased light output as seen in figure \ref{fig:lightoutput-20}. These measurements have lower individual CTR errors than the previous 30 mm measurements, likely due to a greater number of $\gamma\gamma$ events recorded. These being approximately 5000 for LSO:CeCa compared to 3400 for LYSO:Ce, where these numbers are taken from figures \ref{fig:confinement-20} and \ref{fig:confinement} respectively. As the volume of the confinement region within the scintillator crystal is the same in both measurements this difference is primarily due to the difference in measurement time. 

From table \ref{tab:doictrresults-20} the mean CTR for the wrapped configuration is $198\pm2$ ps. In comparison an identical scintillator detector has a CTR of 176$\pm$7 ps for the standard coincidence measurement given in [Table 2]\cite{uffray_Jarron_Meyer_Lecoq_2014}. From table \ref{tab:standardctr}, for an equivalent $2\times2\times20$ mm$^3$ Proteus LYSO:Ce scintillator crystal a CTR of 202.7$\pm$4.0 ps in standard coincidence is observed. Therefore we see that LSO:CeCa is a superior material to that of LYSO:Ce. We also see that the CTR is worse in the DOI timing coincidence apparatus than in the standard. This conclusion is in agreement with the 30 mm measurements where we see values of 209.6$\pm$3.8 ps for the standard coincidence and 231.7$\pm$2.9 ps in the DOI coincidence apparatus. These are the two closest values from their respective experiments, indicating a minimum degradation of 10$\pm$2\%. As the components and SiPM parameters are the same in both the standard and DOI coincidence apparatus, we would conclude this difference is due to the confinement region.